---
title: "Machine Learning"
author: ''
date: "20 June 2015"
output: pdf_document
---
###Level-1 Reading Raw data from the directory
```{r,echo=FALSE}
setwd("/home/wissen/Coursera_Machine Learning/Course_project/")
library(caret)
library(rattle)
library(randomForest)
set.seed(1)
training<-read.csv("pml-training.csv",na.strings=c("NA","#DIV/0!", ""))
testing<-read.csv("pml-testing.csv",na.strings =c("NA","#DIV/0!", ""))
```
###Level-2 Preprocessing: Removing columns with NA's and removing the first 6 coloumns which are not much useful.
```{r}
training<-training[,colSums(is.na(training)) == 0]
training<-training[,-c(1:7)]
testing<-testing[,-c(1:7)]
```
###Level-3 Creating training and testing set from the training data set, we are partitio in the ration of 75:25.
```{r}
intrain<-createDataPartition(y=training$classe,p=0.75,list=FALSE)
training_data<-training[intrain,]
testing_data<-training[-intrain,]
```
### Level-4 Training the model using the training_data set.
```{r}
model2<-randomForest(classe~.,data=training_data,method="class")
```
### Using the model we are doing prediction on the testing_data and comparing the actual output and the predicted output
```{r,echo=FALSE}
prediction2<-predict(model2,testing_data,type="class")
dt2<-data.frame(predicted=prediction2,actual=testing_data$classe)
head(dt2)
```
### Cross Validation
```{r,echo=FALSE}
confusionMatrix(prediction2,testing_data$classe)
```
##Submission Part
```{r,echo=FALSE}
predict1<-predict(model2,testing)
print(predict1)
```